\thesistitle

### 2019-07-15 sections/research.tex
T2R flow

\subsubsection{Comparing Statements/Declarations}
In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor. Whether two nodes in this graph are duplicates of each other is dependent on the clone type. In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.

@@

>>>>

\subsubsection{Comparing Statements/Declarations} \label{sec:comparingstuff}
In the previous section we described a ``duplicate'' relation between nodes in the clone graph built by CloneRefactor. Whether two nodes in this graph are duplicates of each other is dependent on the clone type. In this section, we will describe for each type how we compare statements and declarations to assess whether they are clones of each other.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CloneRefactorT2RFlow}
  \caption{Process used to check the variability threshold for T2R clones.}
  \label{fig:clonerefactort2rflow}
\end{figure}

Figure \ref{fig:clonerefactort2rflow} shows the steps that CloneRefactor performs to find clones conforming with the type 2R variability threshold. This process is done as a postprocessing step after clone detection. The type 2R clone determination process is described in more detail in section \ref{sec:comparingstuff}.
